---
title: "MSDS 534 Statistical Learning Project (11/11/2020)"
author: "Christopher Rabeony"
date: "11/16/2020"
output:
  word_document: default
  html_document: default
---
## Data Attributes
* `age` - age in years.
* `sex` - gender (0 = male; 1 = female)
* `cp` - chest pain type 
    + `1` = typical agina 
    + `2` = atyptical angina 
    + `3` = non-anginal pain
    + `4` = asymptomatic
* `trestbps` - resting blood pressure (in mm HG)
* `chol` - serum cholestoral in mg/dl
* `fbs` - fasting blood sugar > 120 mg/dl (0 = false; 1 = true)
* `restecg` - resting electrocardiographic results
    + `0` = normal 
    + `1` = having ST-T Wave abnormal (T wave inversions and/or ST elevation or depression of > 005 mV)  
    + `2` = showing probable or definite left vetricular hyptertropy
* `thalach` - maximum heart rate achieved in beats per minute (bpm)
* `exang` - exercise induced angina (0 = no; 1 = yes)
* `oldpeak` - ST depression induced by exercise relative to rest
* `slope` - the slope of the peak exercise ST segment
    + `1` - upsloping
    + `2` - flat
    + `3` - down-sloping
* `ca` - number of major vessels (0-3) colored by fluoroscopy
* `thal` - displays the thalassemia
    + `3` = normal 
    + `6` = fixed defect 
    + `7` = reversible defect
* `goal` - predicted target variable. Diagnosis of heart disease (angiographic disease status) 
    + `0` = < 50% diameter narrowing 
    + `1` = > 50% diameter narrowing)

```{r}
# Set up libraries
#library(pastecs)
# Definition for clean tables
#options(scipen=100)
#options(digits=3)
# Read the data into a data frame
heart <- read.csv("E:/School/Statistical Learning for Data Science/Project/processed.cleveland (1).data", header = F)
```

#### Clean up our data.
```{r, warning=FALSE}
names(heart) <- c("age", "sex", "cp", "trestbps", "chol", "fbs", "restecg", "thalach", "exang", "oldpeak", "slope", "ca", "thal", "goal")#naming columns for convenience
heart$ca <- as.integer(heart$ca)# manipulating the data for analysis
heart$thal <- as.integer(heart$thal)
heart$goal[heart$goal == 2] <- 1
heart$goal[heart$goal == 3] <- 1
heart$goal[heart$goal == 4] <- 1
summary(heart)# checking mean, meadian, and number of NAs in table
sapply(heart, sd, na.rm = TRUE)# checking standard deviations in table

heart_matrix <- matrix(unlist(na.omit(heart)), nrow = 297, ncol= 14)# setting up for mass independence testing
colnames(heart_matrix) <- c("age", "sex", "cp", "trestbps", "chol", "fbs", "restecg", "thalach", "exang", "oldpeak", "slope", "ca", "thal", "goal")
ind<-combn(NCOL(heart_matrix),2) # setting up combinations for testing indepence

heartchi <- apply(ind, 2, function(ind) chisq.test(heart_matrix[, ind[1]], heart_matrix[, ind[2]]))# perfoming chi square indpendence tests
heartchip <- data.frame(heartchi[[1]]$p.value)# extracting pvalue to start data fram
heartchip

for(i in 2:NROW(heartchi))# filling out table using loop
{
    heartchip <- cbind(heartchip, heartchi[[i]]$p.value)
}
heartchip <- t(heartchip)# transposing loop for formatting

heartchi2<-cbind(t(ind), heartchi)# combining relevant tables for final display
heartchi2<-cbind(heartchi2, heartchip[,1])
heartchi2 #final product

lmheart <- glm(goal~., heart, family = "binomial")# creating basic, preliminary logistic model
summary(lmheart)
```

